Constraining Quiescent Supermassive Black Hole Environments.

### 2014-08-31 ms.tex
Some reorganization

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{natbib}

\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

@@

In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.  The accretion rate in turn has implications for rate of black hole growth.

@@

We also explore the effects of varying the heating rate on the flow structure. Typically an inflow outflow flow structure is established. The stellar ejecta inside of the stagnation radius ($\rs$) will be accreted, while that outside $\rs$ will be driven out with the outflow. The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.  
%In fact, as the specific thermal energy of the ejects drops below the potential, an inflow is established out to the radius where the SNe Ia rate becomes comparable to the dynamical timescale, which for black holes smaller than 10$^8 \Msun$ is well outside the $\rsoi$ 
%It turns out that in our models the mass accretion rate is coincidentally quite similar to the Bondi accretion rate.

@@

@@

This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

@@

%%AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this 
number will lie in the range $\sim$0.1-1. We adopt $\eta=1$. However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.

$v_w^2/2$ encapsulates heating in our simulation. We take $v_w^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.

\section{Solutions}
\subsection{Analytics: Location of Stagnation Radius}
It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density at $\rs$.

Consider the steady-state entropy equation.

\begin{align}
&\rho T v \dsdr=\Q\\
&\dsdr=\frac{\Q}{\rho T v} \label{eq:ss_entropy}
\end{align}

At $\rs$, the velocity, $v$ goes to zero.  Therefore, the numerator must also go to 0 at $\rs$. This implies

\begin{align}
 &\kew-\gammaf \cs=0\\
 &\cs=\gammafi \kew\\
 &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}
\end{align}

From the first law of thermodynamics

\begin{align}
T\dsdr&=\ddr{u}+p\ddr{(1/\rho)}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho^2}\ddr{\rho}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho} \underbrace{\dxdy{\log{\rho}}{\log{r}}}_{-n} \label{eq:first_law}
\end{align}

Combining Equation~\ref{eq:first_law} and Equation~\ref{eq:ss_entropy}, one obtains.

\begin{align}
\frac{1}{\gamma-1}\ddr{(p/\rho)}+r n \cs=\frac{\Q}{\rho  v} \label{eqn:combo1}
\end{align}

At the stagnation point we also have (from the momentum equation)

\begin{align}
&\frac{1}{\rho}\dpdr=-\dphidr\\
&\ddr{(p/\rho)}-r n \cs=-\dphidr \label{eqn:HSE}
\end{align}

Then multiplying Equation~\ref{eqn:HSE}  $\frac{1}{\gamma-1}$ and subtracting it from Equation~\ref{eqn:combo1} we obtain

\begin{align}
\gammaf r n \cs = \frac{1}{\gamma-1} \dphidr + \frac{\Q}{\rho  v}
\end{align}

From the above equation we may obtain an expression for the Stagnation point using L'Hopital's rule and Equation~\ref{eq:tstag}. To obtain an analytic expression, we take $\Mstar\sim r^{2-\Gamma}$

\begin{align}
&\kewO n =A \phirs -B \frac{G \Mbh}{\rs}\\
&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
\end{align}

Note that in the above expression $\Mstar$ is evaluated at the stagnation radius. Let $\omega=\Mstar(\rs)/\Mbh$ and 
$\eta=v_{w,0}/\sigma_{\rm soi}$. We may re-parameterize this relationship as follows:

\begin{align}
\x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
\end{align}

Note that in general $\omega$ is an implicit function of $x$. Cusp galaxies have $\Gamma\simeq1$.  Then $\omega=x$. With $\gamma=5/3$, $A=2$ and $B=1/4$.  Then:

\begin{align}
\x=\frac{7-2n}{2\eta^2 n+2n-8}
\end{align}

Consider the limit $\lim_{\eta \to 0}$ (the extra heating $\vwO$ goes to 0. Then we will get a negative value for the stagnation radius unless the gas density profile is quite steep at the $\rs$: $3.5<n<4$...

In contrast for a core galaxy we will have $\Gamma\simeq0, A=9/4, B=1/2$, and  $\omega=x^2$. Thus we will have a quadratic equation for stagnation radius, which gives

\begin{align}
\x=\frac{\eta^2 n \pm \sqrt{\eta^4 n^2 -4 \left(\frac{9}{4}-\frac{n}{2}\right) \left(\frac{7}{4}-\frac{n}{2}\right)}}{2\left(\frac{9}{4}-\frac{n}{2}\right)}
\end{align}

Consider the limit $\lim_{\eta \to 0}$, then for $\rs$ to exist we must have $3.5<n<4.5$.

@@

\begin{align}
\kewO=\frac{7}{4}\frac{G \Mbh}{n \rs}
\label{eq:stag_simple}
\end{align}

Where the pre-factor on the right-hand side is valid for $\gamma=5/3$ and $\Gamma=1$ or 0.

@@

\begin{align}
\vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}}
\end{align}

@@

The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.  Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating. Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds. On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe. These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
\end{enumerate}

\begin{figure}
\includegraphics[width=\columnwidth]{vw_eff.eps}
\caption{\label{fig:vw_eff} Top panel: $\vwO$ vs. $\Mbh/\Msun$ assuming $\vwO$=100 km/s (from main sequence winds) for $\rs/\rIa<1$ and $\vwO$=500 km/s (from type Ia SNes) for $\rs/\rIa>1$. Bottom panel: $\rs/\rIa$ vs. $\Mbh/\Msun$ using heating prescription above.}
\end{figure}

%AG-I am not comfortable saying type Ia SNe's don't contribute to heating for smaller mass BHs. If the cooling time for the SNe is long then it would be wrong to ignore the SNe contribution. The difference would be that the SNe heating would just be less steady.
%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...

@@

>>>>

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
%\usepackage{natbib}

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}

\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}

\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}

\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\pc}{\rm pc}

\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\MbhNorm}{\frac{\Mbh}{10^8 \Msun}}

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\ff}{\rm ff}
\newcommand{\tff}{t_{\ff}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\vwNormB}{\frac{\vwO}{500 \, {\rm km/s}}}
\newcommand{\vwNormC}{\frac{\vwO}{500 \, {\rm km/s}}}

\newcommand{\pyear}{{\rm yr}^{-1}}
\newcommand{\tage}{t_{\rm age}}

@@

In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.  The accretion rate in turn has implications for rate of black hole growth. 
%AG:Perhaps need more detail here.

Constraints on the SMBH accretion rates at the low end of the SMBH mass function also have implications for the black occupation fraction.  For example, \citealt{MillerGallo+:2014a} used an observed relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to constrain the BH occupation fraction.  However, they extrapolate (assuming a single power law) their observed relationship below their detection threshold.  However, it is possible that the $L_x$-$\Mbh$ relationship steepens at smaller $\Mbh$, and thus the black hole occupation fraction could be underestimated at low $\Mbh$. 
%AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold

@@

For each galaxy in our chosen sample, we find a steady state gas profile. Typically an inflow-outflow structure is established. The stellar ejecta inside of the stagnation radius ($\rs$) will be accreted, while that outside $\rs$ will be driven out with the outflow.  It is often assumed that the gas properties at the Bondi radius, $\rb$ set the accretion rate. However, physically it is really $\rs$ which sets the accretion rate. Typically this lies within a factor of a few of the $\rb$.  This means that with perfect knowledge of the gas profile the $\Mdotb$ is typically a good approximation to the actual accretion rate $\Mdot$.  However, using extrapolations of the observed gas temperature and density to estimate $\Mdot$ may cause systematic order of magnitude errors in the inferred  accretion rate.

The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.  Physically, the heating rate of the gas would vary from galaxy to galaxy. For example, SNe Ia may be a large source of energy for the gas. However, this will be only be the case for larger black holes for which the gas inflow time is smaller than the time between successive Ias. Thus, for smaller black holes, the effective gas heating rate may be considerably smaller. Thus, we investigate the effect of changing rate of energy injection on the gas density profiles.

@@

We focus on elliptical galaxies to isolate the effect of mass loss from a relatively old stellar population, avoiding additional gas flowing in from star formation on larger scales.

@@

This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.  The corresponding (spherically symmetric) stellar density, $\rhostar\sim r^{-1-\gamma}$ for $r \ll \rb$ and  $\rhostar\sim r^{-1-\beta}$ for $r \ll \rb$.  $\gamma\simeq1$ for cusp galaxies, while $\gamma\simeq0$ for core galaxies.
%AG:Is there a systematic dependence of beta on galaxy type$.

@@

%%AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this number will lie in the range $\sim$0.1-1 (see Appendix~\ref{app:eta}). We adopt $\eta=1$. However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.

$\vw^2/2$ encapsulates heating in our simulation. We take $\vw^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.

%{\bf NCS: here is some added detail about the role of stellar mass functions in the model}

% if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.  Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.  Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
%
%\begin{figure}
%\includegraphics[width=\columnwidth]{NickPlot.eps}
%\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.  The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.  Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
%\end{figure}
%
%%In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).  We parametrize the wind velocity as 
%\begin{equation}
%\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
%\end{equation}
%The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.  We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.

\section{Solutions}
\subsection{Analytics: Flow properties and $\rs$}
It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density (at $\rs$) $n$.   We summarize the main results here and place the detailed derivation in Appendix~\ref{app:rs}.

The temperature at the $\rs$ is given by

\begin{align}
 &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
 &T=6 \times 10^6 {\rm K} \, \mu \, \left({\frac{\vw}{500 \,{\rm km/s}}}\right)^2 
\end{align}

We may also write an (implicit) analytic expression for $\rs$ itself. Let $\omega=\Mstar(\rs)/\Mbh$ and  $\eta=v_{w,0}/\sigma_{\rm soi}$.

\begin{align}
\x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
\label{eq:stag_analytic}
\end{align}

@@

\begin{align}
&\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
&\simeq 6 \, \pc \left(\MbhNorm\right) \left(\vwNormB\right)^{-2}
\label{eq:stag_simple}
\end{align}

This relationship will hold as long as $\vw > \sigma(\rsoi)$, or equivalently (from the $M-\sigma$ relationship) $\vwO > \left(\frac{\Mbh}{10^8 \Msun}\right)^{1/5} 200 {\rm \,  km/s}$.

$\Mdot$ flowing towards the hole is given by

\begin{align}
\dot{M}=\frac{\eta \Menc(\rs)}{\rs}
\end{align}

In physical units this may be approximated as

\[
\dot{M}
\begin{cases}
   1.5 \time 10^{-3}  \left(\MbhNorm\right)^{1.9} \left(\vwNormB\right)^{-4} \Msun \, \pyear& \text{for core galaxies} \\
   3.3 \times 10^{-3}   & \text{for cusp galaxies}      
\end{cases}
\label{eq:cooling}
\]

Finally, we may estimate the $\rho$ at $\rs$, using

\begin{equation}
\rho(\rs)\simeq q(\rs) \tff
\end{equation}

@@

\begin{align}
\vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}
\end{align}

@@

The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.  Above $\sim10^8 \Msun$ SNes will represent an important contribution to the overall heating. 
%Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds. On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe. These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
%\end{enumerate}

\item \emph{Overall Heating Rate}
The overall value of $\vwO$ has contributions from Type Ia SNes  and main sequence winds.  The relative
contributions will depend on both the age of the stellar population, $t_{\rm age}$ and $\Mbh$.  This is
illustrated in Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe Ia will not contribute to 
$\vwO$ as the flow time scale is short compared to $t_{\rm Ia}$, and the heating is dominated by main
sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for $\Mbh \gsim 10^8 \Msun$, heating
from Ias becomes important, as $\rs>\rIa$.  In this regime, we add the $\vwO$ values from SNe Ias and from
main sequence winds in quadrature. $\vwO$ from SNe Ia's depends on the rate of mass loss ($\eta$), which is
in turn a function of $t_{\rm age}$. This dependence is why the effective $\vwO$ increases with $\tage$ for
large $\Mbh$.

For very young stellar populations ($\tage \lsim 10^7$ years),  $\vwO\simeq 1000$ km/s due to contributions
from line driven winds from high mass main sequence stars.

\begin{figure}
\includegraphics[width=\columnwidth]{vw-contour.eps}
\caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age parameter space.}
\end{figure}

%AG-I am not comfortable saying type Ia SNe's don't contribute to heating for smaller mass BHs. If the cooling time for the SNe is long then it would be wrong to ignore the SNe contribution. The difference would be that the SNe heating would just be less steady.
%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
\end{enumerate}

@@

\appendix
\clearpage
\section{Analytic Expression for the stagnation radius}
\label{app:rs}
\input{appendix}

\section{Dependence of q on stellar age}
\label{app:eta}
\input{eta}
